Cognate beginnings to bilingual lexical acquisition

### 2023-05-25 manuscript/manuscript.qmd
Rename files

We modelled the probability of participants answering each response category (*No* < *Understands* < *Understands and Says*) using a Bayesian, mixed-effects ordinal regression model. This model allowed us to estimate both item and participant word-acquisition trajectories, while estimating the effect of our variables of interest. We added $\text{Age}$ (number of months elapsed between participants' birth date and questionnaire completion), $\text{Length}$ (number of phonemes in the X-SAMPA phonological transcription of the word-form), $\text{Exposure}$ (composite measure of lexical frequency and language degree of exposure), and $\text{Cognateness}$ (a measure of cognateness, defined as the phonological similarity between translation equivalents) as population-level effects, together with their two- and three-way interactions. Predictors were standardised before entering the model by subtracting the mean of the predictor from each value and dividing the result by the standard deviation of the predictor. Participant-level and item-level random intercepts and slopes were included where appropriate, according to the structure of the data [@barr2013random; see @eq-linear]. We specified a weakly informative prior around the parameters of the model (see Appendix C for details).

>>>>

We modelled the probability of participants answering each response category (*No* < *Understands* < *Understands and Says*) using a Bayesian, mixed-effects ordinal regression model. This model allowed us to estimate both item and participant word-acquisition trajectories, while estimating the effect of our variables of interest. We added $\text{Age}$ (number of months elapsed between participants' birth date and questionnaire completion), $\text{Length}$ (number of phonemes in the X-SAMPA phonological transcription of the word-form), $\text{Exposure}$ (composite measure of lexical frequency and language degree of exposure), and $\text{Cognateness}$ (a measure of cognateness, defined as the phonological similarity between translation equivalents) as population-level effects, together with their two- and three-way interactions. Predictors were standardised before entering the model by subtracting the mean of the predictor from each value and dividing the result by the standard deviation of the predictor. Participant-level and item-level random intercepts and slopes were included where appropriate, according to the structure of the data [see @eq-linear, @barr2013random]. We specified a weakly informative prior around the parameters of the model (see Appendix C for details).
